A quantum parallel Markov chain Monte Carlo

### 2022-03-04 main.tex
jasa submission

%\doublespacing

@@

\author{Andrew J.~Holbrook}

\affil{UCLA Biostatistics}

@@

@@

We use the \textsc{R} programming language \citep{rlang} for all simulations and the \textsc{ggplot2} package to generate all figures \citep{ggplot}.  All simulations rely on the fact that the Grover iterations of Equation \eqref{eq:grov} manipulate the probability amplitudes in a deterministic manner. For example, the following \textsc{R} code specifies $N$ uniform probability amplitudes (\verb|sqrtProbs|), performs $I$ Grover iterations and measures a single state according to the resulting probabilities.
\begin{minted}{R}
sqrtProbs <- rep(1/sqrt(N),N); i <- 1
while (i <= I) {
	sqrtProbs  <- -marks*sqrtProbs + (1-marks)*sqrtProbs
	sqrtProbs  <- -sqrtProbs + 2*mean(sqrtProbs)
	i <- i + 1
}
measurement <- sample(size=1, x=1:N, prob=sqrtProbs^2)
\end{minted}
Of course, simulating these iterations on a classical computer, requires precomputing the values of \verb|marks| beforehand.

@@

\bibliographystyle{sysbio}
\bibliography{refs}

>>>>

\doublespacing

@@

%\author{Andrew J.~Holbrook}

%\affil{UCLA Biostatistics}

\author{}

@@

\sloppy
Finally, we compare convergence speed for QPMCMC using 1,000, 5,000 and 10,000 proposals to target a massively multimodal distribution: a mixture of 1,000 2-dimensional, isotropic Gaussians with standard deviations equal to 1 and means equal to $10\times(\boldsymbol{0}, \boldsymbol{1} , \dots , \boldsymbol{999})$. This target is particularly challenging because the distance between modes is significantly larger than standard deviations. In 5 independent simulations, we run each algorithm until it achieves and effective sample size of 100.  Table \ref{tab:res} contains MCMC iterations and target evaluations required to achieve this effective sample size as well as relative speedups over sequential implementations and relative improvements over the 1,000 proposal sampler.

\let\oldtabular\tabular
\let\endoldtabular\endtabular
\renewenvironment{tabular}{\rowcolors{2}{white}{trevorblue!15}\oldtabular}{\endoldtabular}

\newcommand{\ra}[1]{\renewcommand{\arraystretch}{#1}}
\ra{1.2}
\begin{table}[t!]
	\centering
	\resizebox{\textwidth}{!}{
		\begin{tabular}{@{}lllll@{}}\toprule
			Proposals & MCMC iterations  & Target evaluations & Speedup  & Efficiency gain  \\   \midrule
			1,000 & 249,398 (200,998,  311,998) & 24,988,963 (20,149,132, 31,265,011) & 9.98  (9.98, 9.98) & 1  \\   
			5,000 & 14,398 (12,998, 16,998) & 3,314,560 (2,989,418,  3,916,281) & 21.72  (21.70, 21.74) & 7.58  (6.25, 9.71) \\   
			10,000 & 5,998  (4,998,  6,998) & 1,993,484  (1,662,592,  2,330,842) & 30  (29.96, 30.26) & 12.87  (8.64, 18.80) \\    \bottomrule
		\end{tabular}
	}
	\caption{Racing to 100 effective samples for a target with 1,000 disjoint modes. `Speedup' is ratio between target evaluations required for sequential and quantum implementations. `Efficiency gain' is ratio between target evaluations required for 1,000 proposal and 5,000/10,000 proposal implementations. We report means (minima, maxima) across 5 independent runs.}\label{tab:res}
\end{table}

@@

We use \textsc{R} \citep{rlang}, \textsc{Python} \citep{vanrossum1995python} and \textsc{TensorFlow} \citep{abadi2016tensorflow}  in our simulations and the \textsc{ggplot2} package to generate all figures \citep{ggplot}.  All simulations rely on the fact that the Grover iterations of Equation \eqref{eq:grov} manipulate the probability amplitudes in a deterministic manner. For example, the following \textsc{R} code specifies $N$ uniform probability amplitudes (\verb|sqrtProbs|), performs $I$ Grover iterations and measures a single state according to the resulting probabilities.
\begin{minted}{R}
sqrtProbs <- rep(1/sqrt(N),N); i <- 1
while (i <= I) {
	sqrtProbs  <- -marks*sqrtProbs + (1-marks)*sqrtProbs
	sqrtProbs  <- -sqrtProbs + 2*mean(sqrtProbs)
	i <- i + 1
}
measurement <- sample(size=1, x=1:N, prob=sqrtProbs^2)
\end{minted}
Of course, simulating these iterations on a classical computer, requires precomputing the values of \verb|marks| beforehand.

@@

\bibliographystyle{chicago}
\bibliography{refs}
